Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-09-13 conclusion.tex
Various edits based on a full pass.
Cut to 11 pages.

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC can still achieve 43\% average coverage.
In addition, with a 1.5x overhead target, IMP shows less than 3\% error on
average.

>>>>

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore the design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC can still achieve 43\% average coverage.
At this overhead target, IMP shows less than 3\% error on average.
With a 1.2x overhead target, LS achieves over 70\% average coverage.

### 2014-09-13 evaluation.tex
Cut to 11 pages.

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with null metadata filtering.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

% BC sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0]{figs/data_bc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for BC.}
    \label{fig:evaluation.bc_sweep}
    \vspace{-0.2in}
  \end{center}
\end{figure}

% UMC sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0]{figs/data_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for UMC.}
    \label{fig:evaluation.umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

% LS sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0]{figs/data_ls_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for LS.}
    \label{fig:evaluation.ls_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

% IMP sweep
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0]{figs/data_imp_sweep.pdf}
    \vspace{-0.2in}
    \caption{Average error vs. varying overhead budget for instruction-mix profiling. Whisker bars show min and max errors.}
    \label{fig:evaluation.imp_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

@@

% Flex UMC sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0]{figs/data_fpga_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage versus varying overhead budget for UMC running on an FPGA-based monitor.}
    \label{fig:evaluation.fpga_umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.2in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0]{figs/data_umc_exec_time.pdf}
    \label{fig:evaluation.umc_exec_time}
  }
  \vspace{-0.2in}
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0]{figs/data_umc_coverage.pdf}
    \label{fig:evaluation.umc_coverage}
  }
  \vspace{-0.1in}
  \caption{Comparing dropping policies for UMC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.umc_policies}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.2in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0]{figs/data_bc_exec_time.pdf}
    \label{fig:evaluation.bc_exec_time}
  }
  \vspace{-0.2in}
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0]{figs/data_bc_coverage.pdf}
    \label{fig:evaluation.bc_coverage}
  }
  \vspace{-0.1in}
  \caption{Comparing dropping policies for BC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.bc_policies}
\end{figure}

@@

% Multi-run coverage with unrestricted dropping
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.2in 0 0]{figs/data_multirun_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage over multiple runs for BC with a 10\% probability to not drop events.}
    \label{fig:evaluation.multirun}
    \vspace{-0.1in}
  \end{center}
\end{figure}

>>>>

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0.1in]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with null metadata filtering.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

% BC sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_bc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for BC.}
    \label{fig:evaluation.bc_sweep}
    \vspace{-0.2in}
  \end{center}
\end{figure}

% UMC sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for UMC.}
    \label{fig:evaluation.umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

% LS sweep
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_ls_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage vs. varying overhead budget for LS.}
    \label{fig:evaluation.ls_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

% IMP sweep
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_imp_sweep.pdf}
    \vspace{-0.2in}
    \caption{Average error vs. varying overhead budget for instruction-mix profiling. Whisker bars show min and max errors.}
    \label{fig:evaluation.imp_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

@@

% Flex UMC sweep
\begin{figure}
  \begin{center}
    \vspace{-0.1in}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_fpga_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage versus varying overhead budget for UMC running on an FPGA-based monitor.}
    \label{fig:evaluation.fpga_umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_umc_exec_time.pdf}
    \label{fig:evaluation.umc_exec_time}
  }
  \vspace{-0.1in}
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_umc_coverage.pdf}
    \label{fig:evaluation.umc_coverage}
  }
  \vspace{-0.1in}
  \caption{Comparing dropping policies for UMC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.umc_policies}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_bc_exec_time.pdf}
    \label{fig:evaluation.bc_exec_time}
  }
  \vspace{-0.1in}
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_bc_coverage.pdf}
    \label{fig:evaluation.bc_coverage}
  }
  \vspace{-0.1in}
  \caption{Comparing dropping policies for BC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.bc_policies}
\end{figure}

@@

% Multi-run coverage with unrestricted dropping
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_multirun_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage over multiple runs for BC with a 10\% probability to not drop events.}
    \label{fig:evaluation.multirun}
    \vspace{-0.1in}
  \end{center}
\end{figure}
